EldersAIR initial PM data work

### 2020-08-10 dustrak_data_cleaning.Rmd
update home and pm data cleaning

# Load, format, and save Dustrak log files
```{r}
## Box location: Update Box location once final data loaded
np_dustrak_initial <- read_xlsx(paste0(file_path, "Input/NP/np_dustrak_20200220.xlsx")) %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         dtid = as.factor(DTID),
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(DTLength),
         sample_ave = as.numeric(DTAverage),
         sample_min = as.numeric(DTMin),
         sample_max = as.numeric(DTMax),
         pm_comments = as.character(Comments),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  select(home_winter_id, area, dtid, sampling_visit, start_date_pm, start_time_pm,
         stop_date_pm, stop_time_pm, sample_obs, sample_ave, sample_min,
         sample_max, pm_comments) %>% 
  arrange(home_winter_id)
#write_rds(np_dustrak_initial, paste0(file_path, "Output/np_dustrak.rds"))

## Box location: Update Box location once final data loaded
nn_dustrak_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_dustrak_20200220.xlsx")) %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         dtid = as.factor(DTID),
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(DTLength),
         sample_ave = as.numeric(DTAverage),
         sample_min = as.numeric(DTMin),
         sample_max = as.numeric(DTMax),
         pm_comments = "NA",
         sampling_visit = as.factor(SamplingVisit),
         area = "NN") %>% 
  select(home_winter_id, area, dtid, sampling_visit, start_date_pm, start_time_pm,
         stop_date_pm, stop_time_pm, sample_obs, sample_ave, sample_min,
         sample_max, pm_comments) %>% 
  arrange(home_winter_id)
#write_rds(nn_dustrak_initial, paste0(file_path, "Output/nn_dustrak.rds"))

elders_dustrak_log <- rbind(np_dustrak_initial, nn_dustrak_initial)
#write_rds(elders_dustrak_log, paste0(file_path, "Output/elders_dustrak_log.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds")) %>% 
  filter(winter_id == 1 | winter_id == 2)

elders_dustrak_log_new <- elders_dustrak_log %>% 
  left_join(elders_ids_linked, by = c("area", "home_winter_id")) %>% 
  arrange(home, winter_id)
#write_rds(elders_dustrak_log_new, paste0(file_path, "Output/elders_dustrak_log.rds"))
```

@@

### NN ###
# List files
list_text_files <- list.files(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/text"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/text")) # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = " ", skip = 28)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
nn_pm_text_space <- initial_data %>% 
  separate(file_name, c("home", "trash"), sep = 7, remove = FALSE) %>% 
  mutate(home = as.character(home),
         date_pm = mdy(`MM/dd/yyyy`),
         time_pm = as.character(`hh:mm:ss`),
         pm = as.numeric(`mg/m^3`),
         area = "NN",
         file_type = "text",
         winter_id = 1) %>% 
  unite("datetime", c("date_pm", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_pm = ymd_hms(datetime)) %>% 
  select(home, area, winter_id, datetime_pm, date_pm, time_pm, pm, file_type) %>% 
  filter(!is.na(pm)) %>% 
  ungroup() %>% 
  arrange(area, home, datetime_pm)

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/text")) # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = ",", skip = 28)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
nn_pm_text_comma <- initial_data %>% 
  separate(file_name, c("home", "trash"), sep = 7, remove = FALSE) %>% 
  mutate(home = as.character(home),
         date_pm = mdy(`MM/dd/yyyy`),
         time_pm = as.character(`hh:mm:ss`),
         pm = as.numeric(`mg/m^3`),
         area = "NN",
         file_type = "text",
         winter_id = 1) %>% 
  unite("datetime", c("date_pm", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_pm = ymd_hms(datetime)) %>% 
  select(home, area, winter_id, datetime_pm, date_pm, time_pm, pm, file_type) %>% 
  filter(!is.na(pm)) %>% 
  ungroup() %>% 
  arrange(area, home, datetime_pm)

### NP ###
# List files
list_text_files <- list.files(paste0(file_path, "Input/NP/np_dustrak/pre_20200218/text"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NP/np_dustrak/pre_20200218/text")) # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = ",", skip = 29,
                            col_names = c("date", "time", "pm"))) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
np_pm_text_comma <- initial_data %>% 
  separate(file_name, c("home", "trash"), sep = 7, remove = FALSE) %>% 
  mutate(home = as.character(home),
         date_pm = mdy(date),
         time_pm = as.character(time),
         pm = as.numeric(pm),
         area = "NP",
         file_type = "text",
         winter_id = 1) %>% 
  unite("datetime", c("date_pm", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_pm = ymd_hms(datetime)) %>% 
  select(home, area, winter_id, datetime_pm, date_pm, time_pm, pm, file_type) %>% 
  filter(!is.na(pm)) %>% 
  ungroup() %>% 
  arrange(area, home, datetime_pm)

@@

### NN ###
# List files
list_csv_files <- list.files(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/csv"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/csv")) # set new working directory
initial_data = tibble(file_name = list_csv_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
nn_pm_csv <- initial_data %>% 
  mutate(trash1 = `Instrument Name`,
         trash2 = `DustTrak II`) %>% 
  select(file_name, trash1, trash2) %>% 
  group_by(file_name) %>% 
  mutate(date = if_else(trash1 == "Test Start Date", trash2,"NA"),
         time = if_else(trash1 == "Test Start Time", trash2,"NA")) %>% 
  arrange(date, time) %>% 
  mutate(time = lead(time),
         date = first(date),
         time = first(time),
         elapsed_time = as.numeric(trash1)) %>% 
  filter(!is.na(elapsed_time)) %>% 
  #separate(time, c("time", "trash3"), sep = " ") %>% 
  unite(datetime, c("date", "time"), sep = " ") %>% 
  mutate(pm = as.numeric(trash2),
         datetime = mdy_hms(datetime),
         datetime_pm = datetime + seconds(elapsed_time)) %>% 
  separate(datetime_pm, c("date", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(date_pm = ymd(date),
         area = "NN",
         file_type = "csv",
         winter_id = 1) %>% 
  ungroup() %>% 
  separate(file_name, c("home", "trash"), sep = 7, remove = FALSE) %>% 
  select(home, area, winter_id, datetime_pm, date_pm, time_pm, pm, file_type) %>% 
  filter(!is.na(pm)) %>% 
  arrange(area, home, datetime_pm)

### NP ###
# List files
list_csv_files <- list.files(paste0(file_path, "Input/NP/np_dustrak/pre_20200218/csv"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NP/np_dustrak/pre_20200218/csv")) # set new working directory
initial_data = tibble(file_name = list_csv_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
np_pm_csv <- initial_data %>% 
  mutate(trash1 = `Instrument Name`,
         trash2 = `DustTrak II`) %>% 
  select(file_name, trash1, trash2) %>% 
  group_by(file_name) %>% 
  mutate(date = if_else(trash1 == "Test Start Date", trash2,"NA"),
         time = if_else(trash1 == "Test Start Time", trash2,"NA")) %>% 
  arrange(date, time) %>% 
  mutate(time = lead(time),
         date = first(date),
         time = first(time),
         elapsed_time = as.numeric(trash1)) %>% 
  filter(!is.na(elapsed_time)) %>% 
  #separate(time, c("time", "trash3"), sep = " ") %>% 
  unite(datetime, c("date", "time"), sep = " ") %>% 
  mutate(pm = as.numeric(trash2),
         datetime = mdy_hms(datetime),
         datetime_pm = datetime + seconds(elapsed_time)) %>% 
  separate(datetime_pm, c("date", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(date_pm = ymd(date),
         area = "NP",
         file_type = "csv",
         winter_id = 1) %>% 
  ungroup() %>% 
  separate(file_name, c("home", "trash"), sep = 7, remove = FALSE) %>% 
  select(home, area, winter_id, datetime_pm, date_pm, time_pm, pm, file_type) %>% 
  filter(!is.na(pm)) %>% 
  arrange(area, home, datetime_pm)

##### Bind files from above #####
elders_pm <- rbind(nn_pm_csv, nn_pm_text_comma, nn_pm_text_space,
                   np_pm_csv, np_pm_text_comma) %>% 
  arrange(area, home, datetime_pm) %>% 
  ungroup()
# Save pm dataset as RDS 
# write_rds(elders_pm, paste0(file_path, "Output/elders_pm_full_raw.rds"))
```

>>>>

# Load, format, and save Dustrak log files
```{r}
np_dustrak_initial <- read_xlsx(paste0(file_path, "Input/NP/dusttrack.xlsx"),
                                skip = 1, na = c("", "NULL"),
                                col_names = c("home_winter_id", "dtid", "file_name",
                                              "dt_cleaned", "dt_zeroed", "pm_comments",
                                              "start_date", "start_time",
                                              "stop_date", "stop_time",
                                              "sample_interval", "sample_obs",
                                              "sample_ave", "sample_min", "sample_max",
                                              "sampling_visit", "dt_qaqc"),
                                col_types = c("text", "text", "text",
                                              "text", "text", "text",
                                              "date", "date",
                                              "date", "date",
                                              "text", "numeric",
                                              "numeric", "numeric", "numeric",
                                              "text", "text")) %>% 
  # rename variables
  separate(start_time, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(stop_time, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.factor(home_winter_id),
         dtid = as.factor(dtid),
         start_date_pm = ymd(start_date),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(stop_date),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(sample_obs),
         sample_ave = as.numeric(sample_ave),
         sample_min = as.numeric(sample_min),
         sample_max = as.numeric(sample_max),
         sampling_visit = as.factor(sampling_visit),
         area = "NPT") %>% 
  select(home_winter_id, area, dtid, sampling_visit, start_date_pm, start_time_pm,
         stop_date_pm, stop_time_pm, sample_interval, sample_obs, sample_ave, sample_min,
         sample_max, pm_comments) %>% 
  arrange(home_winter_id)

nn_dustrak_initial <- read_xlsx(paste0(file_path, "Input/NN/dusttrack.xlsx"),
                                skip = 1, na = c("", "NULL"),
                                col_names = c("home_winter_id", "dtid", "file_name",
                                              "dt_cleaned", "dt_zeroed", "pm_comments",
                                              "start_date", "start_time",
                                              "stop_date", "stop_time",
                                              "sample_interval", "sample_obs",
                                              "sample_ave", "sample_min", "sample_max",
                                              "sampling_visit", "dt_qaqc"),
                                col_types = c("text", "text", "text",
                                              "text", "text", "text",
                                              "date", "date",
                                              "date", "date",
                                              "text", "numeric",
                                              "numeric", "numeric", "numeric",
                                              "text", "text")) %>% 
  # rename variables
  separate(start_time, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(stop_time, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.factor(home_winter_id),
         dtid = as.factor(dtid),
         start_date_pm = ymd(start_date),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(stop_date),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(sample_obs),
         sample_ave = as.numeric(sample_ave),
         sample_min = as.numeric(sample_min),
         sample_max = as.numeric(sample_max),
         sampling_visit = as.factor(sampling_visit),
         area = "NN") %>% 
  select(home_winter_id, area, dtid, sampling_visit, start_date_pm, start_time_pm,
         stop_date_pm, stop_time_pm, sample_interval, sample_obs, sample_ave, sample_min,
         sample_max, pm_comments) %>% 
  arrange(home_winter_id)

elders_dustrak_log <- rbind(np_dustrak_initial, nn_dustrak_initial)

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))

elders_dustrak_log_new <- elders_dustrak_log %>% 
  left_join(elders_ids_linked, by = c("area", "home_winter_id")) %>% 
  filter(!is.na(home)) %>% 
  select(area, home, home_id_num, home_winter_id, winter_id, sampling_visit, treatment,
         adult_id_num, adult_id_char, dtid:pm_comments) %>% 
  arrange(home, winter_id)

summary(elders_dustrak_log_new)

write_rds(elders_dustrak_log_new, paste0(file_path, "Output/elders_dustrak_log.rds"))
```

@@

### NN ###
# List files
list_text_files <- list.files(paste0(file_path, "Input/NN/nn_dustrak/text"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/text")) # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = " ", skip = 28)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
nn_pm_text_space <- initial_data %>% 
  filter(is.na(`MM/dd/yyyy,hh:mm:ss,mg/m^3`)) %>% 
  mutate(date_pm = mdy(`MM/dd/yyyy`),
         time_pm = as.character(`hh:mm:ss`),
         pm = as.numeric(`mg/m^3`),
         area = "NN",
         file_type = "text") %>% 
  unite("datetime", c("date_pm", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_pm = ymd_hms(datetime)) %>% 
  select(area, datetime_pm, date_pm, time_pm, pm, file_type, file_name) %>% 
  arrange(area, file_name, datetime_pm)

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/text")) # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = ",", skip = 28)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
nn_pm_text_comma <- initial_data %>% 
  filter(is.na(`MM/dd/yyyy hh:mm:ss mg/m^3`)) %>% 
  mutate(date_pm = mdy(`MM/dd/yyyy`),
         time_pm = as.character(`hh:mm:ss`),
         pm = as.numeric(`mg/m^3`),
         area = "NN",
         file_type = "text") %>% 
  unite("datetime", c("date_pm", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_pm = ymd_hms(datetime)) %>% 
  select(area, datetime_pm, date_pm, time_pm, pm, file_type, file_name) %>% 
  arrange(area, file_name, datetime_pm)

### NP ###
# List files
list_text_files <- list.files(paste0(file_path, "Input/NP/np_dustrak/text"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NP/np_dustrak/text")) # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = ",", skip = 29,
                            col_names = c("date", "time", "pm"))) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
np_pm_text_comma <- initial_data %>% 
  mutate(date_pm = mdy(date),
         time_pm = as.character(time),
         pm = as.numeric(pm),
         area = "NPT",
         file_type = "text") %>% 
  unite("datetime", c("date_pm", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(datetime_pm = ymd_hms(datetime)) %>% 
  select(area, datetime_pm, date_pm, time_pm, pm, file_type, file_name) %>% 
  arrange(area, file_name, datetime_pm)

@@

### NN ###
# List files
list_csv_files <- list.files(paste0(file_path, "Input/NN/nn_dustrak/csv"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/csv")) # set new working directory
initial_data = tibble(file_name = list_csv_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
nn_pm_csv <- initial_data %>% 
  mutate(trash1 = `Instrument Name`,
         trash2 = `DustTrak II`) %>% 
  select(file_name, trash1, trash2) %>% 
  group_by(file_name) %>% 
  mutate(date = if_else(trash1 == "Test Start Date", trash2,"NA"),
         time = if_else(trash1 == "Test Start Time", trash2,"NA")) %>% 
  arrange(date, time) %>% 
  mutate(time = lead(time),
         date = first(date),
         time = first(time),
         elapsed_time = as.numeric(trash1)) %>% 
  filter(!is.na(elapsed_time)) %>% 
  #separate(time, c("time", "trash3"), sep = " ") %>% 
  unite(datetime, c("date", "time"), sep = " ") %>% 
  mutate(pm = as.numeric(trash2),
         datetime = mdy_hms(datetime),
         datetime_pm = datetime + seconds(elapsed_time)) %>% 
  separate(datetime_pm, c("date", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(date_pm = ymd(date),
         area = "NN",
         file_type = "csv") %>% 
  ungroup() %>% 
  select(area, datetime_pm, date_pm, time_pm, pm, file_type, file_name) %>% 
  arrange(area, file_name, datetime_pm)

### NP ###
# List files
list_csv_files <- list.files(paste0(file_path, "Input/NP/np_dustrak/csv"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NP/np_dustrak/csv")) # set new working directory
initial_data = tibble(file_name = list_csv_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
np_pm_csv <- initial_data %>% 
  mutate(trash1 = `Instrument Name`,
         trash2 = `DustTrak II`) %>% 
  select(file_name, trash1, trash2) %>% 
  group_by(file_name) %>% 
  mutate(date = if_else(trash1 == "Test Start Date", trash2,"NA"),
         time = if_else(trash1 == "Test Start Time", trash2,"NA")) %>% 
  arrange(date, time) %>% 
  mutate(time = lead(time),
         date = first(date),
         time = first(time),
         elapsed_time = as.numeric(trash1)) %>% 
  filter(!is.na(elapsed_time)) %>% 
  #separate(time, c("time", "trash3"), sep = " ") %>% 
  unite(datetime, c("date", "time"), sep = " ") %>% 
  mutate(pm = as.numeric(trash2),
         datetime = mdy_hms(datetime),
         datetime_pm = datetime + seconds(elapsed_time)) %>% 
  separate(datetime_pm, c("date", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(date_pm = ymd(date),
         area = "NPT",
         file_type = "csv") %>% 
  ungroup() %>% 
  select(area, datetime_pm, date_pm, time_pm, pm, file_type, file_name) %>% 
  arrange(area, file_name, datetime_pm)

##### Read in dusttrack .xlsx files #####

### NN ###
# List files
list_xlsx_files <- list.files(paste0(file_path, "Input/NN/nn_dustrak/csv2"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/csv2")) # set new working directory
initial_data = tibble(file_name = list_xlsx_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
nn_pm_xlsx <- initial_data %>% 
  mutate(trash1 = `Instrument Name`,
         trash2 = `DustTrak II`) %>% 
  select(file_name, trash1, trash2) %>% 
  group_by(file_name) %>% 
  mutate(date = if_else(trash1 == "Test Start Date", trash2,"NA"),
         time = if_else(trash1 == "Test Start Time", trash2,"NA")) %>% 
  arrange(date, time) %>% 
  mutate(time = lead(time),
         date = first(date),
         time = first(time),
         elapsed_time = as.numeric(trash1)) %>% 
  filter(!is.na(elapsed_time)) %>% 
  #separate(time, c("time", "trash3"), sep = " ") %>% 
  unite(datetime, c("date", "time"), sep = " ") %>% 
  mutate(pm = as.numeric(trash2),
         datetime = mdy_hms(datetime),
         datetime_pm = datetime + seconds(elapsed_time)) %>% 
  separate(datetime_pm, c("date", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(date_pm = ymd(date),
         area = "NN",
         file_type = "xlsx") %>% 
  ungroup() %>% 
  select(area, datetime_pm, date_pm, time_pm, pm, file_type, file_name) %>% 
  arrange(area, file_name, datetime_pm)

### NP ###
# List files
list_xlsx_files <- list.files(paste0(file_path, "Input/NP/np_dustrak/csv2"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NP/np_dustrak/csv2")) # set new working directory
initial_data = tibble(file_name = list_xlsx_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

# Format combined file from above; combine with other PM data below
np_pm_xlsx <- initial_data %>% 
  mutate(trash1 = `Instrument Name`,
         trash2 = `DustTrak II`) %>% 
  select(file_name, trash1, trash2) %>% 
  group_by(file_name) %>% 
  mutate(date = if_else(trash1 == "Test Start Date", trash2,"NA"),
         time = if_else(trash1 == "Test Start Time", trash2,"NA")) %>% 
  arrange(date, time) %>% 
  mutate(time = lead(time),
         date = first(date),
         time = first(time),
         elapsed_time = as.numeric(trash1)) %>% 
  filter(!is.na(elapsed_time)) %>% 
  #separate(time, c("time", "trash3"), sep = " ") %>% 
  unite(datetime, c("date", "time"), sep = " ") %>% 
  mutate(pm = as.numeric(trash2),
         datetime = mdy_hms(datetime),
         datetime_pm = datetime + seconds(elapsed_time)) %>% 
  separate(datetime_pm, c("date", "time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(date_pm = ymd(date),
         area = "NPT",
         file_type = "xlsx") %>% 
  ungroup() %>% 
  select(area, datetime_pm, date_pm, time_pm, pm, file_type, file_name) %>% 
  arrange(area, file_name, datetime_pm)

##### Bind files from above #####
elders_pm <- rbind(nn_pm_csv, nn_pm_text_comma, nn_pm_text_space,
                   np_pm_csv, np_pm_text_comma,
                   nn_pm_xlsx, np_pm_xlsx) %>% 
  arrange(area, file_name, datetime_pm) %>% 
  ungroup()

# Save pm dataset as RDS 
write_rds(elders_pm, paste0(file_path, "Output/elders_pm_full_raw.rds"))
```
